---
title: "a5 Data Report"
subtitle: "Mass Shootings"
author: "Bernabe Ibarra"
date: "2019-02-16"
output:
  html_document:
    toc: TRUE
    toc_float: 
      smooth_scroll: TRUE
---

<style>
body{
  font-family: 'Verdana', Georgia;
  font-size: 15px;
  line-height: 25px;
}

h1,h3,h4 {
  font-family: 'Helvetica', Georgia;
}

h1{
  background-color: gray;
  color: #FFFFFF;
  text-shadow: 2px 2px 4px #000000;
  font-family: 'Impact', Georgia;
  padding: 20px;
  text-align: center;
}

.container { width: 1000px; }

h2{
  background-color: #337ab7;
  color: #FFFFFF;
  font-family: 'Heletica', Georgia;
  text-shadow: 1px 1px 2px #000000;
  font-weight: bolder;
  text-indent: 100px; 
}
</style>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F)
source("analysis.R")
```


################################################################################
## Summary information
################################################################################

### How many shootings occurred?
nums shootings:
`r num_shootings`

### The number of lives lost were:
`r lives_lost`

### The total lives impacted(injuries + deaths) were:
`r lives_injured + lives_lost`

### The most impacted cities were:
`r most_impacted_cities`.

### The most impacted states were:
`r most_impacted_states`

<!-- # Data in this paragraph should reference values that you calculate in R, and -->
<!-- # should not simply be typed as text into the paragraph. -->


################################################################################
## Summary Table
################################################################################
<!-- # To show a set of quantitative values to your user, you should include a well -->
<!-- # formatted summary table of your interest. This should not just be the raw data, -->
<!-- # but instead should an aggregate table of information. How you would like to -->
<!-- # aggregate the information (by city, state, month, day of the week, etc.) is up -->
<!-- # to you. Make sure to include accompanying text that describes the important -->

paragraph.

### Most Injured People
```{r}
kable(summary_table, row.names = NA, col.names = c("State", "City", "People Killed", "People Injured"), caption = '*The following table is arranged by descending injuries')
```


################################################################################
## Particular incident
################################################################################
<!-- # Your report will include a paragraph (4+ sentences) of in-depth information -->
<!-- # about a particular (single) incident. You should provide your reader with -->
<!-- # relevant information from the dataset, such as the date and location of the -->
<!-- # incident, as well as the number of people impacted (injured, killed). You -->
<!-- # should include a link to at least one outside resource (not found in the data). -->
<!-- # Data in this paragraph should reference values that you calculate in R, and -->
<!-- # should not simply be typed as text into the paragraph. -->

Paragraph.

### The following incident has the highest deaths observed.
```{r paged.print=TRUE}
kable(most_killed_incident, row.names = NA, col.names = c("Date", "State", "City", "Address", "People Killed", "People Injured"), caption = "*The following incident calculated the max value of people killed")
```

################################################################################
## Interactive map
################################################################################
<!-- # While maps are not always the most appropriate visual representation of -->
<!-- # geographic data, they are extraordinarily popular and attract broad audiences. -->
<!-- # You'll build an interactive map that shows a marker at the location of each -->
<!-- # shooting. On your map, manipulate the appearance (size, color, etc.) of the -->
<!-- # markers based on the underlying dataset (# injured, # killed, etc.). The map -->
<!-- # should be appropriately labeled, and detailed information should be shown to -->
<!-- # the user when they hover over each point. Choice of plotting library is up to -->
<!-- # you, though I suggest you consult the interactive visualization chapter of the -->
<!-- # book -- remember, the map must be interactive, so ggplot2 is probably not the -->
<!-- # best choice. -->


################################################################################
## A plot of your choice
################################################################################
<!-- # In addition to the interactive map, you will build an additional plot of your -->
<!-- # choice. You can do this using the package of your choice, such as ggplot2, -->
<!-- # plotly, bokeh, or others. As you create your chart, be sure to consider what -->
<!-- # questions it answers for your audience. Similarly to your map, you should -->
<!-- # integrate your plot seamlessly with the rest of your report, and -->
<!-- # reference/describe it in your text. Regardless of library, the chart should -->
<!-- # have meaningful and clear title, axis labels, and legend (if appropriate). -->
<!-- # -->
<!-- # You should provide a defense of why you chose the chart by highlighting the -->
<!-- # insights gained from the chart you build. -->
``` {r}
shootings_months_bargraph
```


